Binning Strategies and Related Loss for Large Data

### 2015-04-24 Paper.Rnw
Future work and spell check

\hh{XXX the rest of figure 12 should probably go into a figure 14 - to show that quantile binning and log frequency binning yield very similar results. We need to fix the legend. Right now they are atrocious (and I am aware that I am responsible for them, so I can say that :) )}

@@

\ktm{Large Data sets of continuous variables are very difficult to visualize in raw form, due to over-plotting of points. Binning allows for the visualization and manipulation of large data sets, and easily translates into binned scatterplots which are more appropriate for the human visual system. Reducing the data for binned scatterplots has distinct computational and visual advantages, however the aggregation comes at the cost of losing precision in the spatial and frequency information. }

@@

\ktm{Spatially binning with smaller bin dimensions will lead to lower spatial losses; however, finer binning requires more processing time and does not highlight large scale density structure. It is left to the plot designer to decide how much spatial information they are willing to sacrific in order to simplify the display of density structure; we do however suggest to err on the side of smaller bins which allow for visualization of finer density structure with lower spatial loss. }

@@

>>>>

%\hh{XXX the rest of figure 12 should probably go into a figure 14 - to show that quantile binning and log frequency binning yield very similar results. We need to fix the legend. Right now they are atrocious (and I am aware that I am responsible for them, so I can say that :) )}

@@

\ktm{Large Data sets of continuous variables are very difficult to visualize in raw form, due to over-plotting of points. Binning allows for the visualization and manipulation of large data sets, and easily translates into binned scatterplots which are more appropriate for the human visual system. Reducing the data for binned scatterplots has distinct computational and visual advantages, however the aggregation can come at the cost of losing precision in the spatial and frequency information. }

@@

\ktm{Spatially binning with smaller bin dimensions will lead to lower spatial losses; however, finer binning requires more processing time and does not highlight large scale density structure. It is left to the plot designer to decide how much spatial information they are willing to sacrifice in order to simplify the display of density structure; we do however suggest to err on the side of smaller bins which allow for visualization of finer density structure with lower spatial loss. }

@@

\ktm{Future implementations of software for constructing binned scatterplots would be well served to allow for choices in specification of binning algorithms. The findings of this research provide suggestions for reasonable default settings for binning parameters that maintain of spatial and frequency information and have desirable visual properties. }
